Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-10-16 paper.tex
coisolation

[Cite Bo Zhang if paper exists].
We showed above in some amazing figure an example where several peptides were co-eluting from the column into that mass-spec within the tolerance used for isolation for fragmentation.
In that particular case, the precursor with m/z dsfadf was chosen for isolation and fragmentation.
In a conventional search, only that precursor mass would be used to select a range of theoretical for comparison.
However, all peptides in that range are co-fragmented and a better solution would be to use all co-isolated precursor masses.
In MetaMorpheus, for each MS2 scan, the corresponding MS1 scan is deconvoluted and the complete list of precursors is gathered for the range surrounding the isolated precursor (+/- 3 Da).
Each deconvoluted mass is used to select a range of theoreticals to use for identification.
The result of this is that often, more than one peptide can be identified from a single MS2 scan.
Below, in Table 3434, we should the number of PSMs for a raw file where we use only a single precursor mass and we compare that to the case where we allow for multiple different precursors.
You can see a significant increase in the number of identified PSMs.
Importantly, you can see in Supplemental Figure erf3e, that the precursor mass errors go down significantly and the standard deviation is much reduced.
This is extremely benficial in both open mass and multi-notch searches because it reduces the number the more difficult to interpret mass shifts and substantially improves G-PTM-D (see below).

@@

MetaMorpheus was programmed to ignore the precursor mass reported by the mass spectrometer in the mass spectrum and instead, deconvolutes all peaks in the MS1 spectrum associated with the tandem mass spectrum to recover all possible precursor masses.
This expanded list of precursors is used in every spectrum match,frequently resulting in multiple peptide identifications from single tandem mass spectrum.

>>>>

[Cite Bo Zhang if paper exists].
We showed above in some amazing figure an example where several peptides were co-eluting from the column into that mass-spec within the tolerance used for isolation for fragmentation.
In that particular case, the precursor with m/z dsfadf was chosen for isolation and fragmentation.
In a conventional search, only that precursor mass would be used to select a range of theoretical for comparison.
However, all peptides in that range are co-fragmented and a better solution would be to use all co-isolated precursor masses.
In MetaMorpheus, for each MS2 scan, the corresponding MS1 scan is deconvoluted and the complete list of precursors is gathered for the range surrounding the isolated precursor ($\pm 3$ Th).
Each deconvoluted mass is used to select a range of theoreticals to use for identification.
The result of this is that often, more than one peptide can be identified from a single MS2 scan.
Below, in Table 3434, we should the number of PSMs for a raw file where we use only a single precursor mass and we compare that to the case where we allow for multiple different precursors.
You can see a significant increase in the number of identified PSMs.
Importantly, you can see in Supplemental Figure erf3e, that the precursor mass errors go down significantly and the standard deviation is much reduced.
This is extremely beneficial in both open mass and multi-notch searches because it reduces the number the more difficult to interpret mass shifts and substantially improves G-PTM-D (see below).

@@

MetaMorpheus was programmed to ignore the precursor mass reported by the mass spectrometer in the mass spectrum and instead, deconvolutes all peaks in the MS1 spectrum associated with the tandem mass spectrum to recover all possible precursor masses.
This expanded list of precursors is used in every spectrum match, frequently resulting in multiple peptide identifications from single tandem mass spectrum.
